---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# adventofcode20

<!-- badges: start -->
<!-- badges: end -->

The goal of adventofcode20 is to ...

## Installation

You can install adventofcode20 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("tjmahr/adventofcode20")
```

But why would you do that?

## Templates

The one thing you might want from this package are the templates:

```{r, eval = FALSE}
use_day(1)
#> Executing: pandoc -t markdown -o 
#> "C:\Users\Tristan\AppData\Local\Temp\RtmpmajieH\file21d052ca5862.markdown" 
#> "C:\Users\Tristan\AppData\Local\Temp\RtmpmajieH\file21d052ca5862.html"
#> √ Writing 'R/day01.R'
#> * Modify 'R/day01.R'
#> ● Write your solution code here
#> ● Once you unlock Part Two, update the Roxygen block with the description
#> √ Writing 'inst/input01.txt'
#> * Modify 'inst/input01.txt'
#> ● Copy your problem input into this file
#> √ Writing 'tests/testthat/test-day01.R'
#> * Modify 'tests/testthat/test-day01.R'
#> ● Write unit tests using the examples from the problem description
#> √ Writing 'inst/run-day01.R'
#> * Modify 'inst/run-day01.R'
#> ● Run your solution on the input here. Once it works, update 
#>   R/data-solutions.R
```

This recipe, called on day 1:

  - downloads the available puzzle description for day 1 into R/day01.R
  - puts the puzzle description into a roxygen documentation block
  - creates placeholder functions for the solutions to day 1
  - creates a unit test for day
  - creates a file to contain the solution for day 1
  - creates a file to hold the input for day 1
